Ellipsoids (v1.0): 3D Magnetic modelling of ellipsoidal bodies

### 2017-05-11 manuscript/manuscript.tex
replace vkj by vjk in equation A1

We present an integrated review of the vast literature
about the magnetic modelling of triaxial, prolate and
oblate ellipsoids.
We also present a theoretical discussion about the
determination of the isotropic susceptibility value above which
the self-demagnetization must be taken into consideration.
We propose an alternative way of determining this value
based on the body shape and the maximum relative error
allowed in the resultant magnetization.
Our approach is an alternative to the constant value which
seems to be determined empirically and
has been used by the geoscientific community.
Our alternative approach is validated
by the results obtained with numerical simulations.
In a future work,
it would be interesting to use a similar approach to
to bound the maximum relative error in the
magnetic field calculated by neglecting the self-demagnetization.

This work also provide a set of routines to model the magnetic
field produced by ellipsoids.
The routines are written in Python language as part of
the Fatiando a Terra \citep{uieda2013}, which is an
open-source library for modelling and inversion in geophysics.
The current version of our code is freely distributed
in a repository of GitHub. We are working to integrate our
routines in the following stable release of Fatiando a Terra.
We hope that these routines be useful to the wide geoscientific
community either in researching and teaching.

@@

Let $\tilde{f}(\tilde{\mathbf{r}})$ be the scalar
function obtained by transforming $f(\mathbf{r})$
(Eq. \ref{eq:f}) from the
main coordinate system (Fig. \ref{fig:orientation-angles}a)
to the local coordinate system (Fig. \ref{fig:orientation-angles}b).
For convenience, let us rewrite Eq.
\ref{eq:coord_transformation} as follows:
\begin{equation}
\tilde{r}_{k} = v_{k1} \, r_{1} + v_{k2} \, r_{2} + v_{k3} \, r_{3} + c_{k} \: ,
\label{eq:r-tilde-k}
\end{equation}
where $\tilde{r}_{k}$, $k = 1, 2, 3$, are the elements of the transformed
position vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation}),
$r_{j}$, $j = 1, 2, 3$, are the elements of the position vector
$\mathbf{r}$ (Eq. \ref{eq:ellipsoid_surface}),
$v_{kj}$, $j = 1, 2, 3$, are the elements of the matrix
$\mathbf{V}$ (Eq. \ref{eq:A}),
and $c_{k}$ is a constant defined by the coordinates
$x_{c}$, $y_{c}$, and $z_{c}$ of the centre of the ellipsoidal body.

>>>>

We present an integrated review of the vast literature
about the magnetic modelling of triaxial, prolate and
oblate ellipsoids.
We also present a theoretical discussion about the
determination of the isotropic susceptibility value above which
the self-demagnetization must be taken into consideration.
We propose an alternative way of determining this value
based on the body shape and the maximum relative error
allowed in the resultant magnetization.
Our approach is an alternative to the constant value which
seems to be determined empirically and
has been used by the geoscientific community.
Our alternative approach is validated
by the results obtained with numerical simulations.
In a future work,
it would be interesting to use a similar approach
to determine bounds for the maximum relative error in the
magnetic field calculated by neglecting the self-demagnetization.

This work also provides a set of routines to model the magnetic
field produced by ellipsoids.
The routines are written in the Python language as part of
the Fatiando a Terra \citep{uieda2013}
open-source library for modelling and inversion in geophysics.
The current version of our code is freely distributed
in a repository hosted on the GitHub website. We are working to integrate our
routines in the next stable release of Fatiando a Terra.
We hope that these routines will be useful to the wide geoscientific
community, either for research or for teaching.

@@

Let $\tilde{f}(\tilde{\mathbf{r}})$ be the scalar
function obtained by transforming $f(\mathbf{r})$
(Eq. \ref{eq:f}) from the
main coordinate system (Fig. \ref{fig:orientation-angles}a)
to the local coordinate system (Fig. \ref{fig:orientation-angles}b).
For convenience, let us rewrite Eq.
\ref{eq:coord_transformation} as follows:
\begin{equation}
\tilde{r}_{k} = v_{1k} \, r_{1} + v_{2k} \, r_{2} + v_{3k} \, r_{3} + c_{k} \: ,
\label{eq:r-tilde-k}
\end{equation}
where $\tilde{r}_{k}$, $k = 1, 2, 3$, are the elements of the transformed
position vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation}),
$r_{j}$, $j = 1, 2, 3$, are the elements of the position vector
$\mathbf{r}$ (Eq. \ref{eq:ellipsoid_surface}),
$v_{jk}$, $j = 1, 2, 3$, are the elements of the matrix
$\mathbf{V}$ (Eq. \ref{eq:A}),
and $c_{k}$ is a constant defined by the coordinates
$x_{c}$, $y_{c}$, and $z_{c}$ of the centre of the ellipsoidal body.
